Dependent Object Types

### 2012-08-05 article.tex
wf

      \infrule[\textsc{tsel-wf$_1$}]
      {\Gamma \ts p \ni \Ldecl L S U \spcomma S \wf \spcomma U \wf}
      {\Gamma \ts p.L \wf}

@@

    \begin{multicols}{2}[\judgement{Well-formed and expanding types}{\fbox{$\Gamma \ts T \wfe$}}]
      \infrule[\textsc{wfe}]
      {\Gamma \ts T \wf \spcomma T \expand_z \seq{D}}
      {\Gamma \ts T \wfe}
    \end{multicols}
}

>>>>

      \infrule[\textsc{tsel-wf$_1$}]
      {\Gamma \ts p \ni \Ldecl L S U \spcomma S \wf \spcomma U \wf}
      {\Gamma \ts p.L \wf \spcomma p.U \wf}

@@

    \begin{multicols}{2}[\judgement{Well-formed and expanding types}{\fbox{$\Gamma \ts T \wfe$}}]
      \infrule[\textsc{wfe}]
      {\Gamma \ts T \wf \spcomma T \expand_z \seq{D}}
      {\Gamma \ts T \wfe}
    \end{multicols}
} % END dot-wf

\subsection*{Well-formedness}

The well-formedness judgement $\Gamma \ts T \wf$ in \figref{dot-wf}
states that in environment $\Gamma$ the type $T$ is
well-formed.

A refinement type $T \refine z {\seq D}$ is
well-formed if the parent type $T$ is well-formed and every
declaration in $\seq D$ is well-formed in an environment augmented by
the binding of the self-reference $z$ to the refinement type itself
(\textsc{rfn-wf}).

A type selection $p.L$ is well-formed if $L$ is a member of $p$, and
the lower bound of $L$ is also well-formed (\textsc{tsel-wf$_1$} and
\textsc{tsel-wf$_2$}). The latter condition has the effect that the
lower bound of a type $p.L$ may not refer directly or indirectly to a
type containing $p.L$ itself --- if it would, the well-formedness
judgement of $p.L$ would not have a finite proof. No such restriction
exists for the upper bound of $L$ if the lower bound is $\bot$
(\textsc{tsel-wf$_2$}). The upper bound may in fact refer back to the
type. Hence, recursive class types and F-bounded abstract types are
both expressible.

The other forms of types in DOT are all well-formed if their
constituent types are well-formed.

Well-formedness extends straightforwardly to declarations with the
judgement $\Gamma \ts D \wf$. All declarations are well-formed if
their constituent types are well-formed.
